Near and mid-infrared properties of known $z\geq5$ Quasars

### 2019-09-11 temp/VHzQ_pre2019/VHzQ_20181108.tex
tex/older_tex/ removed

\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of
a quasar without hot-dust emission in a sample of 21 $z\approx6$
quasars. Such apparently hot-dust-free quasars have no counterparts at
low redshift. Moreover, those authors demonstrate that the hot-dust
abundance in the 21 quasars builds up in tandem with the growth of the
central black hole. But understanding how dust first forms and appears
in the central engine remains an open question.

@@

\vspace{-16pt}
\section{Data}
In Table~\ref{tab:THE_TABLE} we present our dataset and 
we have assembled this in the following manner.  First
we compile the list of all known, spectroscopically confirmed quasars
from the literature. Most of these objects are easily identified by
their broad Ly$\alpha$ emission line, \nv emission and characteristic
shape blueward of 1215\AA\ rest. As we shall see, some of the more
recently discovered objects are close to the galaxy luminosity
function characteristic luminosity $M^{*}$, and some have relatively
weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures
7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
discussion into spectral features and line strengths, and take as given 
the published spectra and identifications.

We then obtain optical, near-infrared and mid-infrared photometry for the
spectral dataset. The optical data comes from the 
Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 
survey \citep{Chambers2016} and the Dark Energy Camera \citep{Flaugher2015}, 
including the Dark Energy Survey \citep[DES;][]{Flaugher2005} and 
the Dark Energy Camera Legacy Survey \citep[DECaLS]{Dey2018}.

Recently, Hyper Suprime-Cam \citep[HSC; ][]{Miyazaki2018} has embarked
on the Subaru Strategic Program \citep[SSP; ][]{Aihara2018a}
delivering exquisite multi-band photometry data
\citep[][]{Aihara2018b} the five broad bands $grizy$.

The near-infrared data comes from two primary sources. First, the Wide
Field Camera \citep[WFCAM; ][]{Casali2007} on the the United Kingdom
Infra-Red Telescope (UKIRT) primarly, but not exclusively as part of
the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.
And second, data from the VIRCAM (VISTA InfraRed CAMera) on the VISTA
\citep[Visible and Infrared Survey Telescope for
Astronomy;][]{Emerson2006, Dalton2006}.

We also obtain mid-infrared, $\lambda=3-30\mu$m wavelength data from the
the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m. 
In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{
\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{wise2.ipac.caltech.edu/docs/release/allwise/}}.

Figure~\ref{fig:filters} displays the wavelength and normalised transmission 
of the filters in question.

@@

\subsection{Near-infrared photometry}~\label{sec:NIR_data} 
Due to their selection of being very faint/undetected in the
observed-frame optical but bright in the observed frame near-infrared,
VH$z$Qs are generally detected in the near-infrared $ZYJHK(s)$-bands
\citep[$\approx$0.83-2.38$\mu$m; e.g., ][]{Peth2011}.

The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
(WFAU) Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
\citep[WSA][]{WSA} and VISTA-VIRCAM, the VISTA Science Archive
\citep[VSA][]{VSA}. These archives were developed for the VISTA Data Flow System
\citep[VDFS][]{VDFS}.

@@

>>>>

\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of
a quasar without hot-dust emission in a sample of 21 $z\approx6$
quasars. Such apparently hot-dust-free quasars have no counterparts at
low redshift. Moreover, those authors demonstrate that the hot-dust
abundance in the 21 quasars builds up in tandem with the growth of the
central black hole. But understanding how dust first forms and appears
in the central engine remains an open question \citep{WangR2008, WangR2011}.

@@

\vspace{-16pt}
\section{Data}
In Table~\ref{tab:THE_TABLE} we present our dataset and we have
assembled this in the following manner.  First we compile the list of
all known, spectroscopically confirmed quasars from the
literature. Most of these objects are easily identified by their broad
Ly$\alpha$ emission line, \nv emission and characteristic shape
blueward of 1215\AA\ in the rest-frame. As we shall see, some of the
more recently discovered objects are close to the galaxy luminosity
function characteristic luminosity $M^{*}$, and some have relatively
weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures
7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
discussion into spectral features and line strengths, and take as
given the published spectra and identifications.

We then obtain optical, near-infrared and mid-infrared photometry for
the spectral dataset. The optical data comes from the Panoramic Survey
Telescope and Rapid Response System (Pan-STARRS) survey
\citep{Chambers2016}. The near-infrared data comes from two sources:
first, the WFCAM \citep[][]{Casali2007} on the UKIRT, primarly, but
not exclusively, as part of the UKIRT Infrared Deep Sky Survey
\citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the VIRCAM on
the VISTA \citep[][]{Emerson2006, Dalton2006}. The mid-infrared,
$\lambda=3-30\mu$m wavelength data is from the the Wide-Field Infrared
Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.

For reference, Figure~\ref{fig:filters} displays the wavelength and normalised transmission 
of the filters in question.

@@

\subsection{Near-infrared photometry}~\label{sec:NIR_data} 
The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
(WFAU) Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
\citep[WSA][]{WSA} and VISTA-VIRCAM, the VISTA Science Archive
\citep[VSA][]{VSA}. These archives were developed for the VISTA Data Flow System
\citep[VDFS][]{VDFS}.

@@

\section{Notes on Individual Objects}
\input{/cos_pc19a_npr/data/highest_z_QSOs/notes_on_individual_objects}

### 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180703.tex
tex/older_tex/ removed

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}

@@

%    \begin{figure}
%      \includegraphics[height=8.0cm,width=8.0cm]
%      {pdf/SDSS_Quasar_Nofz.pdf}
%      \centering
%      \caption[he selection of $z \sim 0.7$ LRGs using the SDSS $riz$-bands]
%              {The selection of $z \sim 0.7$ LRGs using the SDSS $riz$-bands.}
%      \label{fig:fig1}
%    \end{figure}

%    \begin{table}
%    \begin{center}
%    \setlength{\tabcolsep}{4pt}
%    \begin{tabular}{lrrr}
%    Sample Description  & Number in sample & North & South   \\
%    \hline
%    \label{tab:The_LRG_numbers}
%    \end{tabular}
%    \caption{}
%    \end{center}
%    \end{table}

@@

@@

\subsection{Colours}

@@

>>>>

\section*{TO DOs}
\begin{itemize}
\item Urgh, but almost certainly want M$_{\rm BH}$; 
\item May well wanna try and get M$_{\star}$ too...!! ; 
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180613.pdf}
  \centering
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.}
  \label{fig:filters}
\end{figure*}

@@

@@

\begin{table}
  \begin{center}
    \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      Sample Description  & Number in sample & North & South   \\
      \hline
      \label{tab:The_Numbers}
    \end{tabular}
    \caption{}
  \end{center}
\end{table}

@@

\subsection{Colours}
Figure~\ref{fig:Opt_colourredshift} presents the optical
colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.

\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_Optcolors_20180612.pdf}
   \centering
   \caption[]
   {Optical colour-redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.}
   \label{fig:Opt_colourredshift}
 \end{figure*}

Figure~\ref{fig:Opt_colourredshift} presents the near-infrared 
colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180612.pdf}
  \centering
   \caption[]
   {Infrared colour-redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.}
   \label{fig:filters}
 \end{figure*}

@@

\subsection{L-$z$ Plane}
\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/Lz/VHzQ_Lz_20180702.pdf}
  \centering
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.}
  \label{fig:filters}
\end{figure*}

\subsection{SEDs and Dust properties of the VH$z$Qs}
\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/RestWavelength_flux_20180702.pdf}
  \centering
  \caption[]
  {The rest-frame properties of the VH$z$Qs. }
  \label{fig:filters}
\end{figure*}

### 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180704.tex
tex/older_tex/ removed

\section*{TO DOs}
\begin{itemize}
\item Urgh, but almost certainly want M$_{\rm BH}$; 
\item May well wanna try and get M$_{\star}$ too...!! ; 
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180613.pdf}
  \centering
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.}
  \label{fig:filters}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\begin{table}
  \begin{center}
    \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      Sample Description  & Number in sample & North & South   \\
      \hline
      \label{tab:The_Numbers}
    \end{tabular}
    \caption{}
  \end{center}
\end{table}

    \subsection{Very High-$z$ Quasars Detected in WISE}
     \citet{Blain2013}

    \subsubsection{Very High-$z$ Quasars Detected in WISE W3 and W4}

\subsection{Colours}
Figure~\ref{fig:Opt_colourredshift} presents the optical
colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.

\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_Optcolors_20180612.pdf}
   \centering
   \caption[]
   {Optical colour-redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.}
   \label{fig:Opt_colourredshift}
 \end{figure*}

Figure~\ref{fig:Opt_colourredshift} presents the near-infrared 
colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180612.pdf}
  \centering
   \caption[]
   {Infrared colour-redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.}
   \label{fig:filters}
 \end{figure*}

%%\subsection{Mullaney SEDs}

\subsection{Number Density of High-$z$ Sources}

@@

\subsection{L-$z$ Plane}
\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/Lz/VHzQ_Lz_20180702.pdf}
  \centering
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.}
  \label{fig:filters}
\end{figure*}

\subsection{SEDs and Dust properties of the VH$z$Qs}
\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/RestWavelength_flux_20180702.pdf}
  \centering
  \caption[]
  {The rest-frame properties of the VH$z$Qs. }
  \label{fig:filters}
\end{figure*}

@@

@@

\appendix

>>>>

\section*{TO DOs}
\begin{itemize}
\item Almost certainly want to compile M$_{\rm BH}$; 
\item May well wanna try and get M$_{\star}$ too...!! ; 
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
\begin{figure*}
%%trim=l b r t
  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180704.pdf}
  \centering
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.}
  \label{fig:filters}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
 Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta sodales est, vel cursus risus porta non. Vivamus vel pretium velit. Sed fringilla suscipit felis, nec iaculis lacus convallis ac. Fusce pellentesque condimentum dolor, quis vehicula tortor hendrerit sed. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam eu blandit. Donec in lacinia libero.

\subsection{Detection Rates}
\begin{table}
  \begin{center}
    \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      Sample Description  & Number in sample & North & South   \\
      \hline
      \label{tab:The_Numbers}
    \end{tabular}
    \caption{}
  \end{center}
\end{table}

\subsection{Variability}
Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis euismod. Cras vel auctor neque. Nam quis diam risus.

Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu at orci egestas convallis. Aenean quam velit, aliquam vitae viverra in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies nulla. Nullam eu augue id purus mollis dignissim sed et libero. Phasellus eget justo sed neque pellentesque egestas nec id arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel neque id mi ultrices tristique. Integer quam libero, ornare vel gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque cursus, dui nisl egestas augue, non fermentum nisl est nec nisi. Vestibulum nec mi justo, eget dapibus velit.

\subsection{Very High-$z$ Quasars Detected in WISE}
\citet{Blain2013} 
Cras in laoreet mauris. Vivamus nec nulla a dui commodo adipiscing. Proin vulputate lectus nec arcu iaculis sit amet auctor ligula ultricies. Phasellus condimentum gravida tincidunt. Phasellus et mauris ac nibh vestibulum vehicula. Morbi et augue id purus gravida sagittis quis in sem. Phasellus quis risus bibendum eros luctus auctor.

\subsubsection{Very High-$z$ Quasars Detected in WISE W3 and W4}
Proin non tempus velit. Etiam laoreet, enim nec scelerisque dictum, tortor massa tempor enim, id pretium justo quam ac lectus. Maecenas diam nibh, interdum at lobortis sit amet, dignissim et quam. Sed tincidunt faucibus risus, congue tempus nisl consectetur eget. Suspendisse venenatis turpis ut risus aliquam interdum. In at velit sed ligula dictum dignissim ut et dui. Curabitur ac scelerisque purus.

\subsection{Colours}
Pellentesque vel elit neque, in interdum lacus. Quisque sodales, nunc et luctus convallis, nisl dui luctus dui, at congue urna velit a nisl. Ut sit amet sapien a risus dapibus sagittis. Cras sed ultricies erat. Donec id metus sed urna lacinia convallis vel sed enim. Proin nisi libero, ornare vel bibendum eu, sollicitudin sed leo. Cras tincidunt aliquet ultricies. Cras pretium velit leo, in malesuada enim. Duis sagittis ultricies interdum. Proin sit amet sem nec metus feugiat pharetra.

Figure~\ref{fig:Opt_colourredshift} presents the optical
colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.

\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_Optcolors_20180704.pdf}
   \centering
   \caption[]
   {Optical colour vs. spectral type and redshift for Late Type M/L/T dwarfs and the VH$z$Qs.
     The stars are M, L, and T dwarfs from the \citet{Best2018} PS1-detected catalog.  
   {\it N.B. Trying to look as good as Fig.~5 from Best et al. (2018). How does one get 
bigger gaps between subplots??}}
   \label{fig:Opt_colourredshift}
 \end{figure*}

Figure~\ref{fig:Opt_colourredshift} presents the near-infrared 
colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180704.pdf}
  \centering
   \caption[]
   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
     {\it NB} I'm really not sure how Best et al. actually get their stellar sequence so clean. 
There are two types of spectral classification,  but restricting it to just SpT\_optn  or SpT\_nir removes
the blue or red end respectively. Hmmm....}
   \label{fig:filters}
 \end{figure*}

\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_W1W2_W2W3colors_20180407.pdf}
  \centering
   \caption[]
   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
}
   \label{fig:filters}
 \end{figure*}

%\subsection{Number Density of High-$z$ Sources}

@@

\subsection{L-$z$ Plane}
Having obtained an as-near-to-homogenous set of photometry as we can, 
we are now in a position to calculate the Absolute Magnitudes of the VH$z$Q 
sample and in particulare the absolute magnitude at rest-frame 1450\AA'\, $M_{1450}$, 
which is a key physical quantity and goes directly towards the quasar luminosity 
function and thus the reionization of hydrogen calculation.

At $z=5.00$, the rest-frame 1450\AA\ emission is redshifted to 8700\AA\ iobserved, 
i.e., in the $z$-band, while at

\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/Lz/VHzQ_Lz_20180702.pdf}
  \centering
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.}
  \label{fig:filters}
\end{figure*}

\subsection{SEDs and Dust properties of the VH$z$Qs}
There are a range of IR SEDs e.g. \citet{Mullaney2013} etc. etc. etc. 
However, they are, for our purposes all roughly the same.

\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/RestWavelength_flux_20180702.pdf}
  \centering
  \caption[]
  {The rest-frame properties of the VH$z$Qs. }
  \label{fig:filters}
\end{figure*}

@@

This research has made use of the SVO Filter Profile Service
(http://svo2.cab.inta-csic.es/theory/fps/) supported from the Spanish
MINECO through grant AyA2014-55216 
%\citet{} 
The SVO Filter Profile Service\footnote{Rodrigo, C., Solano, E., Bayo, A. http://ivoa.net/documents/Notes/SVOFPS/index.html}
describes the Spanish VO Filter Profile Service. 
The Filter Profile Service Access Protocol. Rodrigo, C., Solano, E. http://ivoa.net/documents/Notes/SVOFPSDAL/index.html

@@

\appendix
\section{Filter Curves} 
FRom the SVO Filter Profile Service\footnote{http://svo2.cab.inta-csic.es/svo/theory/fps/}.
